A pipeline to analyse time-course gene expression data

### 2019-10-15 scripts/manuscript.Rmd
Small modification on the manuscript

```{r fig.width=6, fig.height=6, echo=FALSE}
timely_barplot = function(de_analysis, 
    labels=NULL, qval_threshold=0.05,
    xlab="Timepoint", ylab="Number of DE genes", main="",ylim=c(0, 20000), col="black", ...){
    qval_colnames = colnames(de_analysis)[
	grepl("qval", colnames(de_analysis))]
    if(is.null(labels)){
	labels = sapply(
	    strsplit(gsub("-qval", "", qval_colnames), "\\."), .subset2, 3)
    }
    number_de_genes_per_time = colSums(de_analysis[, qval_colnames] < 0.05)

@@

```{r fig.height=6, fig.width=6}
cluster2Genes = names(kmeans_clusters$clusters[kmeans_clusters$clusters==2])
dataToPlot=rbind(y[cluster2Genes[3:6], ],"Centroid"=kmeans_clusters$centroids[2,])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

# Let's keep only the list of genes that have a label.
labels = unlist(labels[!is.na(labels)])
cluster2Score = names(labels[labels==2])
```

@@

Of the four genes we plotted before, `r sum(cluster2Genes[3:6] %in% cluster2Score)` of them remained assigned to cluster 2. We can again look at a few genes in cluster 2, only now pick the best scoring genes

```{r fig.height=6, fig.width=6}
# order them by their score
cluster2Score = cluster2Score[order(scores_and_labels$scores[cluster2Score, 8], decreasing = TRUE)]
dataToPlot = rbind(data[cluster2Score[1:4], ],"Centroid"=kmeans_clusters$centroids[8, ])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

**EAP: I don't know what to think about these plots -- these are best scoring, but pretty noisy. Also the per-gene spline is sometimes not as good of a explanation as the cluster centroid. It's seems like an important plot to make**

**Nelle: in my experience, the large the cluster is, the noisier the centroid
estimation is. I've switched to cluster 8, as this is the cluster we focus our
interpretation, and the top scoring genes seem to be to be closely related to
the centroid estimates**

@@

Using the bootstrapping strategy we sample with replacement a sample of the
same size as our original clustering (i.e. `r dim(y)[1]` genes):

@@

**EAP: So this is very confusing to understand, because you read the results from a file (`stability_5.tsv`), but I don't know what this file contains, nor how they were calculated. And I don't know what a stability matrix is -- you've only talked about a consensus matrix. There should be the code here for a single k, but not evaluated, and say that for convenience we provide the results of running this code as a file for users to play with. I've tried to fix up the text to be what I think it should be**

>>>>

```{r fig.width=6, fig.height=6, echo=FALSE}
timely_barplot = function(de_analysis, 
    labels=NULL, qval_threshold=0.05,
    xlab="Timepoint", ylab="Number of DE genes", main="", ylim=c(0, 20000), col="black", ...){

    qval_colnames = colnames(de_analysis)[
	grepl("qval", colnames(de_analysis))]
    if(is.null(labels)){
	labels = sapply(
	    strsplit(gsub("-qval", "", qval_colnames), "\\."), .subset2, 3)
    }
    number_de_genes_per_time = colSums(de_analysis[, qval_colnames] < 0.05)

@@

```{r fig.height=6, fig.width=6}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
dataToPlot=rbind(y[cluster2Genes[3:6], ],"Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

# Let's keep only the list of genes that have a label.
labels = unlist(labels[!is.na(labels)])
cluster2Score = names(labels[labels==cluster_of_interest])
```

@@

Of the four genes we plotted before, `r sum(cluster2Genes[3:6] %in%
cluster2Score)` of them remained assigned to cluster `r cluster_of_interest`. We can again look at a
few genes in cluster `r cluster_of_interest`, only now pick the best scoring genes

```{r fig.height=6, fig.width=6}
# order them by their score
cluster2Score = cluster2Score[order(scores_and_labels$scores[cluster2Score, cluster_of_interest],
				    decreasing = TRUE)]
dataToPlot = rbind(data[cluster2Score[1:4], ],"Centroid"=kmeans_clusters$centroids[cluster_of_interest, ])
plot_splines_data(dataToPlot, moanin_model,
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

**EAP: I don't know what to think about these plots -- these are best scoring, but pretty noisy. Also the per-gene spline is sometimes not as good of a explanation as the cluster centroid. It's seems like an important plot to make**-

@@

@@

Using the bootstrapping strategy, we sample with replacement a sample of the
same size as our original clustering (i.e. `r dim(y)[1]` genes):

@@
